---
title: "p8105_hw1_mnw2132"
author: "Mary Williams"
date: "2024-09-18"
output: github_document
---

## Problem 1 
**Download the package and load the dataset**
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(palmerpenguins)
library(ggplot2)
library(tidyverse)
```

install.packages("palmerpenguins")

data("penguins", package = "palmerpenguins")

**Description of penguins data set**

*Data in the set, including names/values of important variables*

The columns names are `r colnames(penguins)`.

An overall summary of the data includes `r summary(penguins)`.

*Size of the data*
The data set includes `r nrow(penguins)` rows, made up of individual penguins, and `r ncol(penguins)` columns, made up of different variables. 

*Mean flipper length*
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

**Make a scatterplot**

```{r scatterplot}
ggplot (data=penguins, aes(x= bill_length_mm, y= flipper_length_mm, color=species))+geom_point()

ggsave("flippervsbill_scatterplot.png")
```

## Problem 2
**Create the data frame**
```{r dataframes}
Q2 <- tibble(
  randomsample = rnorm(10),
  greater_than_zero = rnorm(10) > 0,
  character = letters[1:10],
  factor = factor(sample(c("Level_1","Level_2","Level_3"), 10, replace = TRUE)))
```
**Calculate the means**
```{r mean}
mean(pull(Q2,randomsample))
mean(pull(Q2,greater_than_zero))
mean(pull(Q2,character))
mean(pull(Q2,factor))
```
The mean for the character vector and the factor vector received an answer of "NA" because they are not numeric and therefore cannot have a mean calculated. 

**Use as.numeric on logical, character and factor variables**
```{r as.numeric, eval=FALSE}
mean(as.numeric(pull(Q2,greater_than_zero)))
mean(as.numeric(pull(Q2,character)))
mean(as.numeric(pull(Q2,factor)))
```

The logical variables get coded as 1 or 0, which causes the mean=0.5. Meanwhile, the factor variable gets coded in regard to the levels of 1-3, thereby creating a mean of 2. However, the character variables get changed into NA's by coercion, therefore a mean still cannot be calculate as the variables are NA. 