---
title: "p8105_hw1_mnw2132"
author: "Mary Williams"
date: "2024-09-18"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(palmerpenguins)
```

## Problem 1 
**Download the package and load the dataset**
install.packages("palmerpenguins")

data("penguins", package = "palmerpenguins")

**Description of penguins data set**

*Data in the set, including names/values of important variables*

The columns names are `r colnames(penguins)`.

An overall summary of the data includes `r summary(penguins)`.

*Size of the data*
The data set includes `r nrow(penguins)` rows, made up of individual penguins, and `r ncol(penguins)` columns, made up of different variables. 

*Mean flipper length*
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

**Make a scatterplot**
install.packages("ggplot2")
library(ggplot2)

*Create a data frame containing variables for our plot.*
```{r scatterplot}
library(ggplot2)
library(palmerpenguins)
library(tidyverse)

ggplot (data=penguins, aes(x= bill_length_mm, y= flipper_length_mm, color=species))+geom_point()

ggsave("flippervsbill_scatterplot.png")
```

## Problem 2
**Create the dataframe**
```{r dataframes}
library(tidyverse)
df<- tibble(
  randomsample=rnorm(10),
  greater_than_zero=rnorm(10)>0,
  character=letters[1:10],
  factor=factor(sample(c("A","B","C"),10,replace=TRUE))
)

df
```

**Calculate means for each variable**

```{r means}

mean_randomsample<-mean(df%>% pull(randomsample))
mean_greater_than_zero<-mean(df%>% pull(greater_than_zero))
mean_character<-mean(df%>% pull(character))
mean_factor<-mean(df%>% pull(factor))
```

**Show the means**
```{r show means}
list(
  mean_randomsample = mean_randomsample,
  mean_greater_than_zero = mean_greater_than_zero,
  mean_character = mean_character,
  mean_factor = mean_factor
)
```

Considering that the character and the factor are not numeric or logical, we cannot find the means for them. 